---
title             : "Emotion and Learning Motivation Report"
shorttitle        : "Title"

author: 
  - name          : "Erin Fu"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
latex_engine: xelatex
header-includes:
  - \usepackage{colortbl}
---

```{r setup, include = FALSE}
library(tidyverse)
library(papaja)
library(broom)
library(knitr)
library(tinytex)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
r_refs("r-references.bib")
```

``` {r data preparation}
EM_dataset_wide <- read.csv("data/ErinFu_Dataset_E&M_1114-0125.csv")
EM_dataset_long <- EM_dataset_wide %>%
  pivot_longer(cols = c("Surprise.Important", "Surprise.Interesting", "Surprise.Difficulty", "Surprise.Motivation", "Awe.Important", "Awe.Interesting", "Awe.Difficulty", "Awe.Motivation", "Enjoyment.Important", "Enjoyment.Interesting", "Enjoyment.Difficulty", "Enjoyment.Motivation", "Neutral.Important", "Neutral.Interesting", "Neutral.Difficulty", "Neutral.Motivation", "Fear.Important", "Fear.Interesting", "Fear.Difficulty", "Fear.Motivation", "Sadness.Important", "Sadness.Interesting", "Sadness.Difficulty", "Sadness.Motivation"), 
               names_to = "Name", 
               values_to = "Result") %>%
  separate_wider_delim(Name,
                       delim = ".",
                      names = c("Emotion", "Scale_Type")) %>%
  separate_wider_delim(Result,
                       delim = ".",
                      names = c("Score", "Note"))
write_csv(EM_dataset_long, "data/ErinFu_dataset_E&M_0125.csv")
```

``` {r regression-table, echo=FALSE, results='asis'}
EM_dataset_long$Emotion <- factor(EM_dataset_long$Emotion)
filtered_data_1 <- subset(EM_dataset_long, Scale_Type == "Motivation")
filtered_data_1$Emotion <- relevel(filtered_data_1$Emotion, ref = "Neutral")
regmodel_1 <- lm(Score ~ Emotion + (1|ID), data = filtered_data_1)

regression_results_1 <- tidy(regmodel_1)

regression_table <- regression_results_1 %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  mutate_if(is.numeric, function(x) sprintf("%.3f", x))
knitr::kable(regression_table, format = "markdown", align = "c", caption = "EM Regression Table", label = "regression-table") %>%
  kable_styling(position = "left", latex_options =c("striped", "hold_position")) %>%
  column_spec(5, color = "red", bold = TRUE)
print(regression_table)
```

``` {r emotion-motivation, fig.cap = "Adult's Emotions and Children's Learning Motivation", echo=FALSE}
EM_dataset_long$Score <- as.numeric(EM_dataset_long$Score)
EM_dataset_long %>%
  subset(Scale_Type == "Motivation") %>%
  group_by(Emotion) %>%
ggplot(aes(x = Emotion, y = Score, fill = Emotion)) +
  geom_violin() +
  coord_cartesian(xlim = c(0,7), ylim = c(0,7)) +
  scale_y_continuous(breaks = seq(1, 6, by = 1)) +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 0.6, color = "black", fill = "grey") +
  labs(title = "The Relationship between Adult's Emotions and Children's Learning Motivation", x = "Emotion", y = "Motivation Levels") +
  theme(
    # text = element_text(family = "Times New Roman"),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = 2, size = 0.6),
    panel.grid.major.y = element_line(linetype = 2, size = 0.6)
  )
```

``` {r age-emotion-motivation, fig.cap = "Children's Age and Learning Motivation Grouped by Emotions", echo=FALSE}
EM_dataset_long$Score <- as.numeric(EM_dataset_long$Score)
EM_dataset_long %>%
  subset(Scale_Type == "Motivation") %>%
  group_by(Emotion) %>%
ggplot(aes(x = Child.Age.In.Years, y = Score)) +
  geom_smooth(method = "lm") +
  facet_wrap(.~Emotion, scales = "free_x") +
  scale_y_continuous(breaks = seq(1, 6, by = 1)) +
  geom_point() +
  labs(title = "The Relationship between Children's Age and Learning Motivation", subtitle = 'Grouped by Six Different Emotions', x = "Children's Age (in years)", y = "Motivation Levels") +
  theme(
    # text = element_text(family = "Times New Roman"),
    panel.grid.minor.y = element_blank()
  )
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r Comment(AS15), include=FALSE}
## Descriptive analysis: Demographic data (gender/age/race); Scale scores
## Hypothesis testing analysis: Regression analysis(Emotion*Motivation Score)
## Hypothesis: Different emotions can have a different effect on children's learning motivation (positive emotion can stimulate children's learning motivation, then children who see the facial expression of positive emotions, like awe or enjoyment, will report higher scores in learning motivation)
```

``` {r descriptive-analysis(AS16)}
# Demographic data
EM_dataset_long$Child.Gender <- factor(EM_dataset_long$Child.Gender)
EM_dataset_long$Child.Race <- factor(EM_dataset_long$Child.Race)
EM_dataset_long %>%
  summarize(mean = mean(Child.Age.In.Years),
         median = median(Child.Age.In.Years),
         sd = sd(Child.Age.In.Years),
         range = diff(range(Child.Age.In.Years)))
  summary(EM_dataset_long$Child.Gender)
  summary(EM_dataset_long$Child.Race)
# Scale scores
EM_dataset_long %>%
  group_by(Emotion, Scale_Type) %>%
  summarize(mean = mean(Score),
         sd = sd(Score))
mean_age <- mean(EM_dataset_long$Child.Age.In.Years)
median_age <- median(EM_dataset_long$Child.Age.In.Years)
```

``` {r regression-motivation(AS16), include=FALSE}
EM_dataset_long$Emotion <- factor(EM_dataset_long$Emotion)
filtered_data_1 <- subset(EM_dataset_long, Scale_Type == "Motivation")
filtered_data_1$Emotion <- relevel(filtered_data_1$Emotion, ref = "Neutral")
regmodel_1 <- lm(Score ~ Emotion + (1|ID), data = filtered_data_1)

regression_results_1 <- tidy(regmodel_1)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Literature Review  
## Positive Emotions  
Positive emotions refer to emotional responses that express positive affect [@vandenbos_apa_2007].The most common positive emotions are “well-being” and “happiness” [@lewis_handbook_2008]. Early psychological research did not place as much emphasis on positive emotions as compared to negative emotions [@sauter_more_2010]. First, positive emotions were not as clearly categorized as negative emotions, which made it difficult to conduct relevant research. This is because positive emotions have less cognitive distinction and are therefore more likely to occur more than one of them simultaneously [@lewis_handbook_2008; @tong_differentiation_2015]. In addition, many positive emotions have very similar facial expressions (e.g., smiling), making it difficult for researchers to recognize the types of positive emotions through facial signals [@fredrickson_value_2003]. As a result, many previous studies tend to focus on "happiness" as the only positive emotion [@keltner_taxonomy_2021; @sauter_more_2010]. Second, positive emotions are rarely associated with specific behavioral tendencies [@lewis_handbook_2008]. Positive emotions tend to be more diffuse and less intense than negative emotions, making them difficult to observe directly in experiments [@baumeister_bad_2001; @fredrickson_open_2008]. Finally, positive emotions were considered as not directly linked to the cause of many important psychological disorders [@lewis_handbook_2008], such as depression and anxiety. This also leads to less attention on positive emotions since they seem to have less research value compared to negative emotions.  
However, in recent years, research on positive emotions and their effects has gradually gained more attention. With the development of relevant theories and face recognition techniques, more and more facial signals of positive emotions have been distinguished and categorized [@revord_categorizing_2021; @girard_reconsidering_2019]. For example, Shiota, Campos, and Keltner [-@shiota_faces_2003] showed that different positive emotions can correspond to distinguished and specific facial muscle movements. The development of categorizing positive emotions has led to more diverse directions in the study of them. At the same time, although positive emotions are not as urgent and intense as negative emotions, they can have a long-term and lasting impact on life [@snyder_oxford_2009, Chapter 3]. This impact is felt in a variety of ways, including promoting physical and mental health [@fredrickson_value_2003], improving community and organizational relationships [@diener2020positive], stimulating creativity and motivation [@bono_charisma_2006], and so on. Researchers have also noted the role of positive emotions in alleviating negative mental states. For example, experiencing a certain level of positive emotions can help people recover from bereavement more quickly [@tedlie_moskowitz_positive_2003]. Many psychological methods associated with enhancing positive emotions have also become non-clinical interventions for treating mental disorders such as depression [@silton_regulating_2020]. As a result, positive mood is no longer only studied as an outcome, but rather as a predictor or influencer in research [@lewis_handbook_2008].  

## Learning Motivation  
In recent 40 years, learning motivation received plenty of attention in research fields [@mayer_handbook_2011]. Learning motivation is considered one of the initial structures of motivation in education [@amrai_relationship_2011] and is closely related to behaviors that lead to learning [@tokan_effect_2019]. For example, learning motivation can influence continuous learning, such as how much time a learner will spend on a specific subject [@hartnett_importance_2016]. It is also considered to be one of the most important factors in driving learners to accomplish learning goals [@filgona_motivation_2020]. In addition, learning motivation has a positive correlation with learning outcomes [@lin_study_2017]. For children, learning motivation can be a strong predictor for both academic achievement and specific skills [@baker_dimensions_1999; @pakarinen_classroom_2010]. For example, according to a meta-analysis by Quílez-Robres et al. [-@quilez-robres_motivational_2021], learning motivation was positively associated with math achievement, reading skills, and student goals. This also emphasizes the importance of enhancing learning motivation in the teaching and learning process.   
Several motivation theories were created to explain academic motivation and also its relationship with academic achievement, including self-determination theory [@alivernini_relationship_2011; @kusurkar_how_2013], achievement goal theory [@liem_sociocultural_2012], mindset theory [@chao_rewards_2017] and so on. Among different theories, the self-determination theory created by Richard Ryan and Edward Deci [-@deci_handbook_2004] is one of used most widely in studies. In Self-Determine Theory, or SDT, different types of motivation are distinguished by the reason for raising an action [@deci_general_1985]. Intrinsic and extrinsic motivation are the two most basic categories of motivation. The former arises from doing something for internal dynamics, such as interesting or enjoyable, while the latter stems from doing something for external outcomes [@ryan_intrinsic_2000].   
Countless studies show a close relationship between intrinsic motivation and learning behaviors or academic outcomes. A meta-analysis [@taylor_self-determination_2014] values intrinsic motivation as the most important type of motivation that influences academic achievement. Students with higher intrinsic motivation tend to have higher classroom engagement or put more effort into their learning, which makes them more likely to achieve better grades [@guthrie_contributions_2007; @walker_identification_2006]. Given this importance, intrinsic motivation always received closer attention in previous research. It is worth mentioning that, however, there are also internal dynamics can also be found in some extrinsic motivations. Ryan and Deci [-@ryan_intrinsic_2020] further refined extrinsic motivation into four types, and identification and integration are two that are relatively internalized. In this case, the type of motivation is not only determined by where they come from, but more importantly, the degree of autonomy. [@ryan_intrinsic_2020].   
Autonomy is defined as one of the three basic psychological needs in self-determination theory, which refers to a person's feeling of controlling and endorsing his or her behavior [@ryan_self-regulation_2006]. It is also one of the key factors in stimulating goal-directed behaviors [@wang_competence_2019]. In learning, autonomy is considered a predictor for a variety of key educational outcomes [@ryan_intrinsic_2020]. Research shows that is beneficial in increasing exploratory behaviors and improving learning outcomes [@wielenga-meijer_costs_2011]. How to increase and support students' autonomy has also been the topic of much educational research [@jang_engaging_2010; @stephenson_supporting_1998]. The researchers’ focus on autonomy reflects its importance in the field of education. More importantly, satisfying autonomy may lead to enhanced motivation [@meng_live_2015]. Specific to the field of education, providing a learning environment that supports autonomy can cultivate learning motivation [@garcia_effects_1996]. For example, students who thought their instructor allowed students to participate in course decisions felt more autonomy, and reported higher learning motivation at the end of the semester. Therefore, it is reasonable to assume that for motivation, the role of autonomy is more than just categorization but prediction.  
Previous research has given plenty of elements that can influence the level of autonomy. According to Patall et al.'s research [-@patall_student_2013], people experience more autonomy when performing or choosing a behavior out of interest. In addition, people feel a relatively high degree of willingness and control when identifying with the importance of tasks [@ryan_intrinsic_2020]. Finally, task difficulty might influence self-efficacy [@hughes_learner-controlled_2013], which plays an important role in developing autonomy [@duchatelet_fostering_2019]. In this case, our study plans to measure students’ autonomy from three measurements: 1) interest, 2) importance, and 3) difficulty, and further explore whether they can be predictors of learning motivation.


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results
Here is my table: \@ref(tab:regression-table)  
Here is my first graph: \@ref(fig:emotion-motivation)   
Here is my second graph: \@ref(fig:age-emotion-motivation)  

The mean age is `r round(mean_age, 3)` years and the median age is `r median_age` years.

Table 1 is the table of the regression model: \@ref(tab:regression-table). Taking the emotion of awe as an example, we compare its influence to learning motivation with the intercept (Neutral). As we can see in the second line, $b$ = `r regression_results_1$statistic[[2]]` ($p$ `r apa_p(regression_results_1$p.value[[2]], add_equals = TRUE)`). In this case, we tend to believe awe as a positive emotion can significantly influence learning motivation.

We can also find in this table that the $b$ value of Fear is `r regression_results_1$statistic[[4]]` and the $b$ value of Sadness is `r regression_results_1$statistic[[5]]`. This means compared with our baseline, they have negative influence on learning motivation.



# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
