---
title             : "Emotion and Learning Motivation Report"
shorttitle        : "Title"

author: 
  - name          : "Erin Fu"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
latex_engine: xelatex
header-includes:
  - \usepackage{colortbl}
---

```{r setup, include = FALSE}
library(tidyverse)
library(papaja)
library(broom)
library(knitr)
library(tinytex)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
r_refs("r-references.bib")
```

``` {r data preparation}
EM_dataset_wide <- read.csv("data/ErinFu_Dataset_E&M_1114-0125.csv")
EM_dataset_long <- EM_dataset_wide %>%
  pivot_longer(cols = c("Surprise.Important", "Surprise.Interesting", "Surprise.Difficulty", "Surprise.Motivation", "Awe.Important", "Awe.Interesting", "Awe.Difficulty", "Awe.Motivation", "Enjoyment.Important", "Enjoyment.Interesting", "Enjoyment.Difficulty", "Enjoyment.Motivation", "Neutral.Important", "Neutral.Interesting", "Neutral.Difficulty", "Neutral.Motivation", "Fear.Important", "Fear.Interesting", "Fear.Difficulty", "Fear.Motivation", "Sadness.Important", "Sadness.Interesting", "Sadness.Difficulty", "Sadness.Motivation"), 
               names_to = "Name", 
               values_to = "Result") %>%
  separate_wider_delim(Name,
                       delim = ".",
                      names = c("Emotion", "Scale_Type")) %>%
  separate_wider_delim(Result,
                       delim = ".",
                      names = c("Score", "Note"))
write_csv(EM_dataset_long, "data/ErinFu_dataset_E&M_0125.csv")
```

``` {r regression-table, echo=FALSE, results='asis'}
EM_dataset_long$Emotion <- factor(EM_dataset_long$Emotion)
filtered_data_1 <- subset(EM_dataset_long, Scale_Type == "Motivation")
filtered_data_1$Emotion <- relevel(filtered_data_1$Emotion, ref = "Neutral")
regmodel_1 <- lm(Score ~ Emotion + (1|ID), data = filtered_data_1)

regression_results_1 <- tidy(regmodel_1)

regression_table <- regression_results_1 %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  mutate_if(is.numeric, function(x) sprintf("%.3f", x))
knitr::kable(regression_table, format = "markdown", align = "c", caption = "EM Regression Table", label = "regression-table") %>%
  kable_styling(position = "left", latex_options =c("striped", "hold_position")) %>%
  column_spec(5, color = "red", bold = TRUE)
print(regression_table)
```

``` {r emotion-motivation, fig.cap = "Adult's Emotions and Children's Learning Motivation", echo=FALSE}
EM_dataset_long$Score <- as.numeric(EM_dataset_long$Score)
EM_dataset_long %>%
  subset(Scale_Type == "Motivation") %>%
  group_by(Emotion) %>%
ggplot(aes(x = Emotion, y = Score, fill = Emotion)) +
  geom_violin() +
  coord_cartesian(xlim = c(0,7), ylim = c(0,7)) +
  scale_y_continuous(breaks = seq(1, 6, by = 1)) +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 0.6, color = "black", fill = "grey") +
  labs(title = "The Relationship between Adult's Emotions and Children's Learning Motivation", x = "Emotion", y = "Motivation Levels") +
  theme(
    # text = element_text(family = "Times New Roman"),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(linetype = 2, size = 0.6),
    panel.grid.major.y = element_line(linetype = 2, size = 0.6)
  )
```

``` {r age-emotion-motivation, fig.cap = "Children's Age and Learning Motivation Grouped by Emotions", echo=FALSE}
EM_dataset_long$Score <- as.numeric(EM_dataset_long$Score)
EM_dataset_long %>%
  subset(Scale_Type == "Motivation") %>%
  group_by(Emotion) %>%
ggplot(aes(x = Child.Age.In.Years, y = Score)) +
  geom_smooth(method = "lm") +
  facet_wrap(.~Emotion, scales = "free_x") +
  scale_y_continuous(breaks = seq(1, 6, by = 1)) +
  geom_point() +
  labs(title = "The Relationship between Children's Age and Learning Motivation", subtitle = 'Grouped by Six Different Emotions', x = "Children's Age (in years)", y = "Motivation Levels") +
  theme(
    # text = element_text(family = "Times New Roman"),
    panel.grid.minor.y = element_blank()
  )
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r Comment(AS15), include=FALSE}
## Descriptive analysis: Demographic data (gender/age/race); Scale scores
## Hypothesis testing analysis: Regression analysis(Emotion*Motivation Score)
## Hypothesis: Different emotions can have a different effect on children's learning motivation (positive emotion can stimulate children's learning motivation, then children who see the facial expression of positive emotions, like awe or enjoyment, will report higher scores in learning motivation)
```

``` {r descriptive-analysis(AS16)}
# Demographic data
EM_dataset_long$Child.Gender <- factor(EM_dataset_long$Child.Gender)
EM_dataset_long$Child.Race <- factor(EM_dataset_long$Child.Race)
EM_dataset_long %>%
  summarize(mean = mean(Child.Age.In.Years),
         median = median(Child.Age.In.Years),
         sd = sd(Child.Age.In.Years),
         range = diff(range(Child.Age.In.Years)))
  summary(EM_dataset_long$Child.Gender)
  summary(EM_dataset_long$Child.Race)
# Scale scores
EM_dataset_long %>%
  group_by(Emotion, Scale_Type) %>%
  summarize(mean = mean(Score),
         sd = sd(Score))
mean_age <- mean(EM_dataset_long$Child.Age.In.Years)
median_age <- median(EM_dataset_long$Child.Age.In.Years)
```

``` {r regression-motivation(AS16), include=FALSE}
EM_dataset_long$Emotion <- factor(EM_dataset_long$Emotion)
filtered_data_1 <- subset(EM_dataset_long, Scale_Type == "Motivation")
filtered_data_1$Emotion <- relevel(filtered_data_1$Emotion, ref = "Neutral")
regmodel_1 <- lm(Score ~ Emotion + (1|ID), data = filtered_data_1)

regression_results_1 <- tidy(regmodel_1)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Literature Review  
Positive emotions refer to emotional responses that express positive affect [@vandenbos2007apa].The most common positive emotions are “well-being” and “happiness” [@fredrickson2008positive]. Early psychological research did not place as much emphasis on positive emotions as compared to negative emotions [@sauter2010more]. First, positive emotions were not as clearly categorized as negative emotions, which made it difficult to conduct relevant research. This is because positive emotions have less cognitive distinction and are therefore more likely to occur more than one of them simultaneously [@fredrickson2008positive; @tong2015differentiation]. In addition, many positive emotions have very similar facial expressions (e.g., smiling), making it difficult for researchers to recognize the types of positive emotions through facial signals [@fredrickson2003value]. As a result, many previous studies tend to focus on "happiness" as the only positive emotion [@keltner2021taxonomy; @sauter2010more]. Second, positive emotions are rarely associated with specific behavioral tendencies [@fredrickson2008positive]. Positive emotions tend to be more diffuse and less intense than negative emotions, making them difficult to observe directly in experiments [@baumeister2001bad; @fredrickson2008open]. Finally, positive emotions were considered as not directly linked to the cause of many important psychological disorders [@fredrickson2008positive], such as depression and anxiety. This also leads to less attention on positive emotions since they seem to have less research value compared to negative emotions.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results
Here is my table: \@ref(tab:regression-table)  
Here is my first graph: \@ref(fig:emotion-motivation)   
Here is my second graph: \@ref(fig:age-emotion-motivation)  

The mean age is `r round(mean_age, 3)` years and the median age is `r median_age` years.

Table 1 is the table of the regression model: \@ref(tab:regression-table). Taking the emotion of awe as an example, we compare its influence to learning motivation with the intercept (Neutral). As we can see in the second line, $b$ = `r regression_results_1$statistic[[2]]` ($p$ `r apa_p(regression_results_1$p.value[[2]], add_equals = TRUE)`). In this case, we tend to believe awe as a positive emotion can significantly influence learning motivation.

We can also find in this table that the $b$ value of Fear is `r regression_results_1$statistic[[4]]` and the $b$ value of Sadness is `r regression_results_1$statistic[[5]]`. This means compared with our baseline, they have negative influence on learning motivation.



# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
